\documentclass[12pt, leqno]{article}
\usepackage{verbatim}
\usepackage[margin=1 in]{geometry}
\usepackage{rotating} %for \let\clearpage\relax\includegraphix[angle=270]
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{bbm}
%\usepackage{amsmath,amssymb,epsfig,amscd,xy,amsthm}
%\xyoption{all}
%\usepackage[active]{srcltx}
%\CompileMatrices
\usepackage{enumerate}
\usepackage{extarrows}
\usepackage{graphicx}
\usepackage{array}
\usepackage{float}\usepackage{tikz-cd}

\usepackage{setspace} \doublespacing

\renewcommand{\contentsname}{Table of Contents}

\usepackage[
    backend=biber,
    style=alphabetic,
]{biblatex}
\addbibresource{refs.bib}

\usepackage{user-commands}
\usepackage{theorem-commands}

\begin{document}
% Title page and title -------------------------------------------------------------------
\begin{titlepage}
\begin{center}

\vspace*{4cm}
\large
\title{Generalized GCDs as Applications of Vojta's Conjecture}
Generalized GCDs as Applications of Vojta's Conjecture

\normalsize
by

Nolan Robert Pyott

\vfill

A thesis

presented to the University of Waterloo

in fulfillment of the

thesis requirement for the degree of

Master of Mathematics

in

Pure Mathematics

\vfill

Waterloo, Ontario, Canada, 2023

\copyright\ Nolan Robert Pyott 2023

\vspace*{2cm}

\end{center}
\end{titlepage}

\newpage

\pagenumbering{roman}
\setcounter{page}{2}

\begin{center}
    \textbf{Author's Declaration}
\end{center}


I hereby declare that I am the sole author of this thesis. This is a true copy of
the thesis, including any required final revisions, as accepted by my examiners.

I understand that my thesis may be made electronically available to the public.

\newpage

% Start of preamble -----------------------------------------------------------
\begin{abstract}
Starting with an analysis of the result that for any coprime integers $a$ and $b$,
and some $\varepsilon > 0$,
we have eventually that $\gcd(a^n - 1, b^n - 1) < a^{\varepsilon n}$ holds for all $n$,
we are motivated to look for geometric reasons why this should hold.
After some discussion on the general geometry and arithmetic needed to examine these questions,
we take a quick look into how Vojta's conjectures provide a generalization of our first result.
In particular, we also note a case where this implies a similar equality on particular elliptic curves.
\end{abstract}

\newpage
\begin{center}
    \textbf{Acknowledgments}
\end{center}

First and foremost, I would like to thank my supervisor Professor David McKinnon for his essential guidance on this thesis.
He enlightened my mathematical perspective on these topics considerably over many meetings and was always someone I knew could be relied upon. 
I'd also like to add a special thanks to my readers, 
Professors Jason Bell and Matthew Satriano,
for their comments and suggestions,
as well as bringing up interesting perspectives regarding this project.
I'm very grateful as well for the support from coordinators Nancy Maloney and Jo-Ann Hardy in their assistance and information which helped me complete this milestone.
I also extend my gratitude to the various staff and students who have helped me along my journey and cultivating my interest in research mathematics.
On my list as well, I thank my colleagues at PostGrid for their understanding and accommodations as I worked to complete this thesis while continuing work.
Lastly, I want to thank my girlfriend Angela for all of her emotional support throughout and helping to maintain our household when times were busy and sleep was short.



\newpage
\tableofcontents
\setcounter{page}{5}

% Start of content ------------------------------------------------------------

\newpage
\pagenumbering{arabic}
\setcounter{page}{1}

\section{Introduction}

\subsection{Overview}
\let\clearpage\relax\include{introduction/overview}

\subsection{An Initial Result}
\let\clearpage\relax\include{introduction/original-result}

\newpage
\section{Geometry}

\subsection{Sheaves}
\let\clearpage\relax\include{geometry-subsections/sheaves}

\subsection{Affine Schemes}
\let\clearpage\relax\include{geometry-subsections/affine-schemes}

\subsection{Schemes and Properties}
\let\clearpage\relax\include{geometry-subsections/schemes-and-properties}

\subsection{Divisors and Sheaves of Modules}
\let\clearpage\relax\include{geometry-subsections/divisors}

\subsection{Blowups}
\let\clearpage\relax\include{geometry-subsections/blowups}

\subsection{Canonical Divisor Class}
\let\clearpage\relax\include{geometry-subsections/canonical-divisor}

\subsection{Elliptic Curves}
\let\clearpage\relax\include{geometry-subsections/elliptic-curves}

\newpage
\section{Height Functions}

\subsection{Projective Height Functions}
\let\clearpage\relax\include{height-subsections/projective-heights}

\subsection{Weil's Height Machine}
\let\clearpage\relax\include{height-subsections/weil-heights}

\subsection{Local Height Functions}
\let\clearpage\relax\include{height-subsections/local-heights}


\newpage
\section{Vojta's Conjecture}
\let\clearpage\relax\include{vojta-subsections/overview}

\newpage
\section{Application to GCD Problems}

\subsection{Generalized GCD}
\let\clearpage\relax\include{application-subsections/generalized-gcd}

\subsection{Main Result}
\let\clearpage\relax\include{application-subsections/main-result}

\subsection{Applications of Main Result}
\let\clearpage\relax\include{application-subsections/applications}

\newpage
\section{Conclusion}
\let\clearpage\relax\include{conclusion}

% References -----------------------------------------------------------------------------
\newpage
\printbibliography
\newpage

\end{document}